Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-07 paper/paper.tex
update values

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 6 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{itemize}
  \item \textbf{Undefined.} Implementation-dependent behavior as per
    ECMA262 specification~\cite{ecmas262-spec}. For example, \Fix{XXX}
  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} Because target engine does not optimize code as the
    original engine did, test fails to finish at the time limit
    specified in the test or runs out of memory. For example, we found
    that only \jsc{} implements tail-call optimization to avoid tail
    recursion.
  \item \textbf{Not implemented.} Test fails because it covers
    function in the spec which is yet to be implemented. For example,
    at the time of writing, Chakra did not implement various
    properties from the \mcodeid{Symbol} object. A test that refers to
    this object will fail in \chakra{}.
  \item \textbf{Future Feature.} Test fails because it uses a feature
    that is available in the original engine, but still not standard,
    and the target engine does not support that feature. For example,
    \Fix{XXX}
  \item \textbf{Error message mismatch.} Test fails because it
    compares an error message, which is not portable across
    engines. For example, \Fix{a test from the engine XXX compares the
      string encapsulated in the object of type YYY. The engine ZZZ
      fails because it produces the string AAA while expecting the
      string BBB.}
\end{itemize}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{itemize}
  \item \textbf{Undefined.} Implementation-dependent behavior as per
    ECMA262 specification~\cite{ecmas262-spec}. For example, \Fix{XXX}
  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} Because target engine does not optimize code as the
    original engine did, test fails to finish at the time limit
    specified in the test or runs out of memory. For example, we found
    that only \jsc{} implements tail-call optimization to avoid tail
    recursion.
  \item \textbf{Not implemented.} Test fails because it covers
    function in the spec which is yet to be implemented. For example,
    at the time of writing, Chakra did not implement various
    properties from the \mcodeid{Symbol} object. A test that refers to
    this object will fail in \chakra{}.
  \item \textbf{Future Feature.} Test fails because it uses a feature
    that is available in the original engine, but still not standard,
    and the target engine does not support that feature. For example,
    \Fix{XXX} \Igor{Creio que neste experimento, essa funcao nao vai 
    aparecer. Identificamos isto em alguns testes da suite test262(nao estamos utilizando ela aqui).}
  \item \textbf{Error message mismatch.} Test fails because it
    compares an error message, which is not portable across
    engines. For example, \Igor{
      a test from the engine \jsc{} uses an assert function called
      \CodeIn{shouldThrow} that expects an specific error message. In this test, 
      all engines throws the Error as expected, however only the message 
      on \jsc{} engine match with the string expected in the test case.
    }
\end{itemize}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
   10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}
